---
title: "Bookkeeping Practice - Unit 2"
---

&nbsp;

### Generate a Question - Type 1 (No Payroll)

<iframe src ="https://mystruth.shinyapps.io/Unit2-Type1/" height=43px width=225px />

```{r Unit2-Type1, echo = FALSE}
knitr::include_app("https://mystruth.shinyapps.io/Unit2-Type1/",
                   height = "42px")
```

The file will automatically download when complete.\
Please be patient when generating! - It can take up to 60 seconds per download



&nbsp;

### Pre-Generated Type 1 Questions

Clicking the below links rewrites the current page so I recommend opening the links in a new tab

[Pre-Generated Question 1](Unit2Type1Pregens/RevisionQuestion-Unit2-Type1 (1).pdf)

[Pre-Generated Question 2](Unit2Type1Pregens/RevisionQuestion-Unit2-Type1 (2).pdf)

[Pre-Generated Question 3](Unit2Type1Pregens/RevisionQuestion-Unit2-Type1 (3).pdf)

[Pre-Generated Question 4](Unit2Type1Pregens/RevisionQuestion-Unit2-Type1 (4).pdf)

[Pre-Generated Question 5](Unit2Type1Pregens/RevisionQuestion-Unit2-Type1 (5).pdf)

[Pre-Generated Question 6](Unit2Type1Pregens/RevisionQuestion-Unit2-Type1 (6).pdf)


&nbsp;


### Generate a Question - Type 2 (With Payroll)

<iframe src ="https://mystruth.shinyapps.io/Unit2-Type2/" height=43px width=225px />

```{r Unit2-Type2, echo = FALSE}
knitr::include_app("https://mystruth.shinyapps.io/Unit2-Type2/",
                   height = "42px")
```

The file will automatically download when complete.\
Please be patient when generating! - It can take up to 30 seconds per download



&nbsp;

### Pre-Generated Type 2 Questions

Clicking the below links rewrites the current page so I recommend opening the links in a new tab

[Pre-Generated Question 1](Unit2Type2Pregens/RevisionQuestion-Unit2-Type2 (1).pdf)

[Pre-Generated Question 2](Unit2Type2Pregens/RevisionQuestion-Unit2-Type2 (2).pdf)

[Pre-Generated Question 3](Unit2Type2Pregens/RevisionQuestion-Unit2-Type2 (3).pdf)

[Pre-Generated Question 4](Unit2Type2Pregens/RevisionQuestion-Unit2-Type2 (4).pdf)

[Pre-Generated Question 5](Unit2Type2Pregens/RevisionQuestion-Unit2-Type2 (5).pdf)

[Pre-Generated Question 6](Unit2Type2Pregens/RevisionQuestion-Unit2-Type2 (6).pdf)
